Test parsing of Proff.no table

### 2022-07-08 Test parsing of Proff table.Rmd
Adding plotly visualisation.

```{r libraries}
library(tidyverse)
library(rvest)
```

@@

Kors |> 
  filter(REGNSKAPSPERIODE == "SUM EGENKAPITAL OG GJELD") |> 
  ggplot(aes(year, value)) +
  geom_col()
```

>>>>

```{r libraries}
library(tidyverse)
library(rvest)
library(plotly)
```

@@

Kors |> 
  filter(REGNSKAPSPERIODE == "SUM EGENKAPITAL OG GJELD") |> 
  ggplot(aes(year, value)) +
  geom_col()

plot <- Kors |> 
  filter(REGNSKAPSPERIODE == "Årsresultat") |> 
  ggplot(aes(year, value)) +
  geom_col()

ggplotly(plot)
```
